Tracing the Stellar Halos of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-06-30 draft/paper1_rachel.tex
Edit final sample and result 1

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure}
      \centering 
      \includegraphics[width=\columnwidth]{fig/redbcg_completeness}
      \caption{
          Evaluation of the \mstar{} completeness of the HSC massive galaxy sample.
          We compare the volume number density function of the massive galaxies 
          for this work (black line) with the one of a much more complete sample
          from the S82-MGC catalog (green line).  
          The associated uncertainties derived from bootstrap resampling are shown in 
          shaded regions. 
          The vertical grey line highlight the \logms{}$=11.6$ limit.  
          Below it, the HSC massive galaxy sample becomes significantly incomplete in 
          stellar mass. 
          }
      \label{fig:mass_complete}
  \end{figure}     
%% ------------------------------------------------------------------------------------ %%

@@

    Although 100 kpc is already a very large radius that should enclose the majority 
    of stars that belong to these massive galaxies, we know that their \mden{} 
    profiles extend beyond 100 kpc without showing any signs of truncation
    (e.g. \citealt{Gonzalez2005, Tal2011, DSouza2014}).
    Therefore, for massive galaxies, even \mtot{} should be only considered a lower
    limit on the ``total'' \mstar{}. 
    In Fig \ref{fig:mass_diff}, we integrate the \mden{} of each galaxy to the edge of 
    the postage-stamp and call this mass \mmax{}. 
    The right panel of Fig \ref{fig:mass_diff} compares \mmax{} and \mtot{}.  
    Uncertainties in the background subtraction, and the impact of neighbouring objects,
    means that \mmax{} is much more uncertain than \mtot{}. 
    Nonetheless, we do see that \mmax{} is larger than than \mtot{}. 
    However, the mass differences are on average very small ($\sim0.02-0.03$ dex) and 
    do not show a strong mass dependence.  
    This confirms that, at the current depth of HSC images, \mtot{} can be used as 
    good proxy of ``total'' stellar mass.

@@

    The robust identification of the central galaxy is not an easy task (e.g.
    \citealt{Yang2007}). 
    In this paper, we use the \redm{} catalog create a sample of massive central 
    galaxies with minimal contamination from satellite galaxies.

%    Given the smaller fraction of satellite galaxies at high-\mstar{} end (e.g. 
%    \citealt{Reid2014, Hoshino2015, Saito2016}), 
%    we further assume that the massive ones (\logmtot{}$>11.4$) among them are likely 
%    to be the central galaxies of these smaller halos.

@@

    Several studies have published calibrations between the \redm{}~richness estimate, 
    $\lambda$, and halo mass (e.g.\ \citealt{Saro2015, Farahi2016, Simet2016, 
    Melchior2016}). 
    All these studies consistently find that \redm{} clusters with $\lambda > 20$ 
    have $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$. 
    Therefore the central galaxies of these \redm{} clusters\footnote{We only use 
    central galaxies with $P_{\mathrm{CEN}} \geq 0.7$} form a sample of massive central 
    galaxies that live in massive halos as described above.
\rachel{Intrinsic scatter in \mhalo{} at fixed $\lambda$ is pretty big, though, so we should be careful about this assertion.}
Such information is also very useful in studying the relationship between galaxy
    structure and environment (Huang\etal in prep.).
%% ------------------------------------------------------------------------------------ %%

@@

    After matching the \texttt{hscZ} sample with the central galaxies of \redm{} 
    clusters with $\lambda \geq 20$ and $P_{\mathrm{Cen}} \geq 0.7$, we find 164 
    matched galaxies at $0.3 \leq z \leq 0.5$.
    This sample of \textbf{central galaxies in more massive halos} will be referred to 
    as the \rbcg{} sample. 
    Due to the depth and resolution of SDSS, the \redm{} catalog becomes slightly 
    incomplete at lower richness ($\lambda < 40$) at $z > 0.33$, but the main results 
    of this work are not affected by this.
    %% Saved as "dr1_redbcg_use_sed5b.fits"

@@

    After removing galaxies associated with \redm{} clusters, the remaining galaxies 
    in our sample will be dominated by central galaxies living in halos with 
    \logmh{}$< 14.0$. 
    We will refer to this sample of \textbf{galaxies in less 
    massive halos} as the \nbcg{} sample. Because we have rejected satellites in \redm{} clusters, and because above our galaxy mass cut most satellites reside in halos with \logmh$>14.0$ (e.g. \citealt{Reid2014, 
    Hoshino2015, Saito2016, vanUitert2016}), galaxies in the \nbcg{} sample should  be dominated by central galaxies.
    \rachel{There is a statistical distribution of halo masses that satellites at this stellar mass live in, based on the papers you cited; can you say more quantitatively what fraction you expect to be satellites in less massive halos?  Right now it all sounds kind of hand-wavey.}

    %% Saved as "dr1_nonbcg_use_sed5b.fits"
%% ------------------------------------------------------------------------------------ %%

@@

    The following is a summary of our sample construction. \rachel{Would be valuable to remind the reader in what sections these samples were defined, and how many galaxies are in each one.}

    \begin{itemize}
        \item \texttt{hscPho} sample: this parent sample consists of bright galaxies 
            with $i_{\mathrm{cModel}} \leq 21.0$, good quality imaging, and reliable 
            \texttt{cModel} photometry in all five HSC bands in the \texttt{S15B} 
            data release. 
        \item \texttt{hscZ} sample: we limit the \texttt{hscPho} sample to galaxies 
            with reliable redshift information. 
        \item With the help of the \redm{} cluster catalog, we further select 
            candidates of massive central galaxies in a range of \mhalo{}.
            We broadly divide the sample into central galaxies living in halos
            with \logmh{}$\geq 14.0$ (\rbcg{}) and \logmh{}$<14.0$ (\nbcg{}). 
    \end{itemize}

    The  division of our sample into two halo mass bins is mainly relevent for Paper II.  For this paper, we only consider the halo mass dependence on our sample when we evaluate impact of  mass estimates on the SMF in Section \ref{ssec:smf}.

\rachel{Could we show the redshift distribution of the second and third of these samples?}

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_mass_smf}
      \caption{
          \textbf{Left:} Impact of using \mtot{} on the galaxy stellar mass function. 
          Dashed lines correspond to the SMF computed using \mcmodel{} whereas solid 
          lines correspond to the SMF computed using \mtot{}. 
          Here we separate our HSC sample into  centrals in halos more massive than
          \logmh{}$\sim14.2$ (red lines) and centrals in halos with \logmh{}$<14.0$ 
          (black lines).
          The impact on the SMF can exceed 0.2 dex for massive central galaxies in 
          very massive halos.
          \textbf{Right}: The stellar mass volume density distributions of massive 
          HSC galaxies, using both \mtot{} (black solid line) and \mmax{} (black dotted 
          line).  
          The grey shaded region shows the resampling error on the HSC SMF plus an additional 20\%
          uncertainty to account for the fact that  we do not include satellite galaxies and that we fail to extract a 1-D profile for xxx\% of our galaxies. These issues will be adressed in forthcoming work. We compare our results with previous studies: 
          (a): SDSS galaxies at $z{\sim} 0.1$ from \citet{Bernardi2017} with \mstar{} 
          values based on photometry from 2-D \ser{}$+$Exponential model fitting 
          (purple); 
          (b): SDSS galaxies at $z{\sim} 0.1$ from \citet{Moustakas13} based on 
          improved SDSS \texttt{cModel} photometry (blue); 
          (c): \texttt{S82-MGC} galaxies at $0.15 < z< 0.43$ from 
          \citet{Leauthaud2016} based on PSF-matched SDSS-UKIDSS photometry (green).
          \rachel{Need to state explicitly what the vertical line is.  I assume this is the stellar mass below which the sample is presumed to be too incomplete for proper derivation of the SMF.  If that's true, should we even be showing masses below that?  Or perhaps the entire left side can be shaded, instead of just having a line there?  Also, are any completeness corrections applied at any value of stellar mass?}}
      \label{fig:smf}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    The Stellar Mass Function (SMF) and its evolution are critical to our understanding of galaxy evolution. On average, the integration of our carefully derived non-parametric \mden{} profile 
    to 100 kpc (\mtot{}) recovers more light (hence mass) than the \texttt{cModel} method. 
    At \logmtot{} $>11.6$, the difference can sometimes be larger than 0.2 dex. 
    More importantly, the average difference steadily increases with \mtot{}. 
    These differences relate to the intrinsic limitation of the \texttt{cModel} 
    method and also reflects the fact that more massive ETGs tend to have more 
    extended stellar mass distributions (e.g. higher-\ser{} index, 
    \citealt{Graham2003}). Hence,  the determination of the ``total luminosities'' of massive galaxies can result in  a significant impact 
    on the high mass end of the galaxy stellar mass function (e.g. 
    \citealt{Bernardi2013, DSouza2014, DSouza2015, Bernardi2017}).

@@

In this paper, we have only measured light profiles for central galaxies. Also,  we cannot extract  a 1-D profile for $\sim 11$\% of galaxies (because contamination from neighbouring galaxies is too severe). These two effects will lead to a ${\sim}20$\% uncertainty in  the amplitude of our SMF.  \rachel{Mass-dependent, or really 20\% at all masses?} These are limitations that we are currently working to address and a forthcoming paper will  address them. Our goal in this paper is therefore not  to  attempt a detailed comparison between different SMFs
    \citep[e.g.,][]{Bernardi2013, Bernardi2017}. Instead, our goal in this section is more simply to characterize the  impact of various \mstar{} measurements  on the high-mass end of the SMF.

     Figure \ref{fig:smf} displays the impact of missing light and of different definitions of \mstar{} on the SMF. The left panel of Fig.~\ref{fig:smf} shows the SMF\footnote{Our SMFs turn over at the low mass end as we have not applied any completeness corrections here. \rachel{Why is this a footnote?  It's a major feature of the plot, not a minor detail.}} computed using \mcmodel{} and \mtot{} for galaxies that live in low and high mass halos.  Figure \ref{fig:smf} shows that the impact of missing flux is more severe for  galaxies in high mass halos. In Paper II it will be demonstrated that this occurs because  galaxies in more massive halos have larger extended  wings than those in low mass halos (Huang\etal in prep.). Figure \ref{fig:smf} also shows that  the use of the HSC \texttt{cModel} magnitude leads to a severe underestimation of the  high mass end of the SMF. 
\rachel{It would be useful if we can say whether this is primarily because of the adoption of simple parametric profiles, or due to background subtraction failures.  For example, if the adoption of simple parametric profiles is the primary cause of this difference, then that is a statement that might be more widely applicable than just the HSC pipeline.  If it's really just because our background subtraction algorithm is bad, then the implications are more limited.  Do we have the information that would allow us to make a statement about this?  If not, we should at minimum reiterate here the possible causes of this discrepancy.}

@@

        As discussed in Section~\ref{ssec:mtotal}, even with our deep HSC images,
    it is non-trivial to clearly define and measure the ``total'' \mstar{} for 
    these massive systems, and the \mden{} profiles of these galaxies often extend 
    well beyond 100 kpc. Is our fiducial 100 kpc radius sufficient in order to capture  most of the flux associated with these galaxies, or does one need to integrate out to even larger radii? To answer this question,  we attempt to capture more flux by integrating our \mden{} profiles out to the detection 
    limit that is defined by the background noise. We will refer to this mass as \mmax{}. Although the \mden{} profiles become more uncertain at $>100$ kpc, \mmax{} helps us quantify how much extra mass may be contained at radii greater than 100 kpc.  The right hand side of Figure \ref{fig:smf} shows the impact of using \mmax{} instead of  \mtot{} on the SMF.  We find that  a 100 kpc radius captures a majority of the galaxy mass and that the impact of going from \mtot{} to \mmax{} is relatively small

@@

        \item The SMF for $0.15 < z < 0.30$ galaxies from the \texttt{S82-MGC} sample
            \citep{Leauthaud2016} where \mstar{} is derived using 
            \texttt{iSEDfit} on PSF-corrected aperture photometry from 
            \texttt{S82}. They adopt the same IMF, dust model, and star-formation model as we do, but use the \texttt{BC03} model. Based on the test results from Appendix \ref{app:sed}, we shift the \citet{Leauthaud2016} SMF by 0.08 dex to add their data to Figure~\ref{fig:smf}.      
        \item The SMF derived from a SDSS-\textit{GALEX} sample of $z{\sim} 0.1$ 
            galaxies from \citet{Moustakas13}.  Total luminosities from \citet{Moustakas13} are based on SDSS \cmodel{} magnitude. 
            They use a \m2l{} that is derived via SED fitting using \texttt{iSEDfit} with similar 
            assumptions as here.
        \item The observed SMF for $z{\sim} 0.1$ SDSS galaxies from 
            \citet{Bernardi2017}.  Total luminosities in  \citet{Bernardi2017} are based on 2-D \texttt{SerExp} models 
            (\ser{}$+$ Exponential disk model; integrated to infinity) that 
            recover more flux compared to SDSS \cmodel{} magnitudes 
            (\citealt{Bernardi2013, Meert2015}). 
            They use a \m2l{} that is adopted from the SED fitting results from the ``dusty'' 
            model in \citet{Mendel2014}. 
            This model also uses the \texttt{FSPS} stellar population model 
            \citep{FSPS} and assumes a \citet{Chabrier2003} IMF. 
    \end{itemize}

    As mentioned above, our current SMF is subject to an additional 20\% uncertainty that will be addressed in forthcoming work. Hence,  we do not attempt a detailed comparison  with respect to previous work on the galaxy SMF, reserving this  for  a future study. Here, we simply note that the  HSC SMF derived using \mtot{} is close to the one derived by \citet{Bernardi2017} using SDSS data at $z{\sim}0.1$ and assuming \texttt{SerExp} models.  Our  sample and the \citet{Bernardi2017} sample have different redshifts. Without a more in-depth study, we cannot ascertain wheter or not  the apparent agreement between the HSC SMF and the  \citet{Bernardi2017} SMF indicates a global lack of evolution in the galaxy SMF, or  that other effects are at play (difference between \mtot{} masses and \texttt{SerExp} masses) that have cancelled redshift evolution.  In future work, it will be interesting to perform a more consistent analysis to search for redshift evolution in the galaxy SMF and to study whether  or not massive galaxies in HSC are well described by \texttt{SerExp} models.

>>>>

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure}
      \centering 
      \includegraphics[width=\columnwidth]{fig/redbcg_completeness}
      \caption{
          Evaluation of the \mstar{} completeness of the HSC massive galaxy sample.
          We compare the volume number density function of the massive galaxies 
          for this work (black line) with the one of a much more complete sample
          from the S82-MGC catalog (green line). 
          The grey dashed line shows the number density function of HSC massive 
          galaxies in the three GAMA fields for comparison.
          The associated uncertainties derived from bootstrap resampling are shown in 
          shaded regions. 
          The vertical grey line highlight the \logms{}$=11.6$ limit.  
          Below it, the HSC massive galaxy sample becomes significantly incomplete in 
          stellar mass. 
          }
      \label{fig:mass_complete}
  \end{figure}     
%% ------------------------------------------------------------------------------------ %%

@@

    Although 100 kpc is already a very large radius that should enclose the majority 
    of stars that belong to these massive galaxies, we know that their \mden{} 
    profiles extend beyond 100 kpc without showing any signs of truncation
    (e.g. \citealt{Gonzalez2005, Tal2011, DSouza2014}).
    Therefore, for massive galaxies, even \mtot{} should be only considered a lower
    limit on the ``total'' \mstar{}. 
    In Fig \ref{fig:mass_diff}, we integrate the \mden{} of each galaxy to the 
    edge of the postage-stamp, and pick the isophote that gives us the highest  
    luminosity to estimate the \mstar{} within and call this one \mmax{}. 
    The right panel of Fig \ref{fig:mass_diff} compares \mmax{} and \mtot{}.  
    Uncertainties in the background subtraction, and the impact of neighbouring objects,
    means that \mmax{} is much more uncertain than \mtot{}. 
    Nonetheless, we do see that \mmax{} is larger than than \mtot{}. 
    However, the mass differences are on average very small ($\sim0.02-0.03$ dex) and 
    do not show a strong mass dependence.  
    This confirms that, at the current depth of HSC images, \mtot{} can be used as 
    good proxy of ``total'' stellar mass.

@@

    Although the central galaxies of dark matter halos have unique importance is 
    studying galaxy-halo connection, robust identification of central galaxy is 
    not easy(e.g.\citealt{Yang2007}) in observation.
    First, based on previous results (\citealt{Reid2014, Hoshino2015, Saito2016}),
    the satellite fraction at \logmtot{}$> 11.6$ should become quite low 
    ($\sim 10$\% level). 
    And, we can further use the \redm{} catalog to identify and exclude massive 
    satellites in cluster-level dark matter halos--to further reduce contamination
    from satellite galaxies.

@@

    Several studies have published calibrations between the \redm{}~richness estimate, 
    $\lambda$, and halo mass (e.g.\ \citealt{Saro2015, Farahi2016, Simet2016, 
    Melchior2016}). 
    All these studies consistently find that \redm{} clusters with $\lambda > 20$ 
    generally have $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$, although the scatter 
    of \mhalo{} at fixed $\lambda$ can not be ignored.
    Therefore the central galaxies of these \redm{} clusters\footnote{We only use 
    central galaxies with $P_{\mathrm{CEN}} \geq 0.7$} form a sample of massive central 
    galaxies that live in massive halos as described above.
    Such information is also very useful in studying the relationship between galaxy
    structure and environment (Huang\etal in prep.).

@@

    After matching the \texttt{hscZ} sample with the central galaxies of \redm{} 
    clusters with $\lambda \geq 20$ and $P_{\mathrm{Cen}} \geq 0.7$, we find 164 
    matched galaxies at $0.3 \leq z \leq 0.5$.
    This sample of \textbf{central galaxies in more massive halos} will be referred to 
    as the \rbcg{} sample. 
    It is also worth pointing out that, due to the depth and resolution of SDSS 
    images, this \redm{} catalog is not complete down to $\lambda=20$ at 
    $0.3 < z < 0.5$. 
    At $z\geq0.33$, it starts to miss a small fraction of clusters with $\lambda < 30$, 
    but the main results of this work will not be affected by this.
    %% Saved as "dr1_redbcg_use_sed5b.fits"

@@

    After removing galaxies associated with \redm{} clusters, the remaining galaxies 
    in our sample will be dominated by central galaxies living in halos with 
    \logmh{}$< 14.0$. 
    We will refer to this sample of \textbf{galaxies in less massive halos} as the 
    \nbcg{} sample. 
    Because we have rejected satellites in \redm{} clusters, and because above our 
    galaxy mass cut most satellites reside in halos with 
    \logmh$>14.0$ (e.g. \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}), 
    galaxies in the \nbcg{} sample should  be dominated by central galaxies.
    Using the model presented in \citet{Saito2016}, we estimate that in dark matter 
    halos with \logmh$<11.4$, $\sim 7$\% of galaxies with \logmcmodel{}$>11.5$ are 
    satellites.
    This confirms that our sample should have low enough satellite contamination 
    so that it can be taken as a sample of massive central galaxy.     
    %% Saved as "dr1_nonbcg_use_sed5b.fits"
%% ------------------------------------------------------------------------------------ %%

@@

    The following is a summary of our sample construction.

    \begin{itemize}
        \item \texttt{hscPho} sample: this parent sample consists of bright galaxies 
            with $i_{\mathrm{cModel}} \leq 21.0$, good quality imaging, and reliable 
            \texttt{cModel} photometry in all five HSC bands in the \texttt{S15B} 
            data release. 
            This sample is described in \S \ref{ssec:initial}, and it contains 
            1760845 galaxies. 
        \item \texttt{hscZ} sample: we limit the \texttt{hscPho} sample to galaxies 
            with reliable redshift information. 
            More details of this sample can also be found in \S \ref{ssec:initial}. 
            It provides us 25286 useful galaxies at $0.3<z<0.5$.
        \item With the help of the \redm{} cluster catalog, we further select 
            candidates of massive central galaxies.
            We broadly divide the sample into central galaxies living in halos
            with \logmh{}$\geq 14.0$ (\rbcg{}) and \logmh{}$<14.0$ (\nbcg{}).
            To ensure the sample is \mstar{}-complete and has minimal satellite 
            contamination, we will further focus on the 950 massive galaxies with 
            \logmtot{}$>11.6$ in this work\footnote{As reference, there are 
            2613 massive galaxies with \logmtot{}$>11.5$ in our sample.}.

    The division of our sample into two halo mass bins is mainly relevant for Paper II
    (Huang \etal in prep.).  
    For this paper, we only consider the halo mass dependence on our sample when we 
    evaluate impact of mass estimates on the SMF in \S \ref{ssec:smf}. 
    We show the distributions of redshift, \mtot{} and \minn{} of the massive galaxy 
    sample in Appendix \ref{app:basic}, along with its \mtot{}-$(g-r)$ rest-frame 
    color relation.

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_mass_smf}
      \caption{
          \textbf{Left:} Impact of using \mtot{} on the galaxy stellar mass function. 
          Dashed lines correspond to the observed volume density distribution 
          computed using \mcmodel{} whereas solid lines correspond to the distribution
          computed using \mtot{}. 
          We do not apply any completeness correction to the distributions here.
          Here we separate our HSC sample into centrals in halos more massive than
          \logmh{}$\sim14.2$ (red lines) and centrals in halos with \logmh{}$<14.0$ 
          (black lines).
          The impact on the SMF can exceed 0.2 dex for massive central galaxies in 
          very massive halos.
          \textbf{Right}: The \mstar{} volume density distributions of massive 
          HSC galaxies, using both \mtot{} (black solid line) and \mmax{} (black dotted 
          line).  
          Vertical lines on both plots highlight the \logmtot{}$=11.6$ mass limit. 
          The grey shaded region shows the resampling error on the HSC SMF plus an
          additional 20\% uncertainty to account for the fact that we do not include 
          satellite galaxies and that we fail to extract a 1-D profile for $\sim 10$\% 
          of our galaxies. 
          These issues will be addressed in forthcoming work. 
          We compare our results with previous studies: 
          (a): SDSS galaxies at $z{\sim} 0.1$ from \citet{Bernardi2017} with \mstar{} 
          values based on photometry from 2-D \ser{}$+$Exponential model fitting 
          (purple); 
          (b): SDSS galaxies at $z{\sim} 0.1$ from \citet{Moustakas13} based on 
          improved SDSS \texttt{cModel} photometry (blue); 
          (c): \texttt{S82-MGC} galaxies at $0.15 < z< 0.43$ from 
          \citet{Leauthaud2016} based on PSF-matched SDSS-UKIDSS photometry (green).
          }
      \label{fig:smf}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    The Stellar Mass Function (SMF) and its evolution are critical to our understanding 
    of galaxy evolution. 
    On average, the integration of our carefully derived non-parametric \mden{} profiles 
    to 100 kpc (\mtot{}) recovers more light (hence mass) than the \texttt{cModel} method. 
    At \logmtot{} $>11.6$, the difference can sometimes be larger than 0.2 dex. 
    More importantly, the average difference steadily increases with \mtot{}. 
    These differences relate to the intrinsic limitation of the \texttt{cModel} 
    method and also reflect the fact that more massive ETGs tend to have more 
    extended stellar mass distributions (e.g. higher-\ser{} index, 
    \citealt{Graham2003}). Hence, the determination of the ``total luminosities'' of 
    massive galaxies can result in a significant impact on the high mass end of the 
    galaxy stellar mass function (e.g. \citealt{Bernardi2013, DSouza2014, DSouza2015,
    Bernardi2017}).

@@

    In this paper, we have only measured light profiles for central galaxies. 
    Also, we cannot extract 1-D profiles for $\sim 11$\% of galaxies (because 
    contamination from nearby bright object is too severe; or the its in a late-stage
    on-going merger system). 
    These two effects will lead to a ${\sim}20$\% uncertainty in the amplitude of 
    our volume number density distributions. 
    Both of these effects show dependence on \mtot{} whereas more massive galaxies 
    suffer slightly less from them.
    We are currently working to address these limitations in a forthcoming paper. 
    Our goal in this paper is therefore not to attempt a detailed comparison between 
    different SMFs \citep[e.g.,][]{Bernardi2013, Bernardi2017}. 
    Instead, our goal in this section is simply to characterize the impact of various 
    \mstar{} measurements on the high-mass end of the SMF.   
    Our volume density distributions (will be referred to as SMF for simplicity) 
    turn over at low-mass end where the sample becomes incomplete, and we do not attempt
    to apply any completeness correction here.

     Figure \ref{fig:smf} displays the impact of missing light and of different 
     definitions of \mstar{} on the SMF. 
     The left panel of Fig.~\ref{fig:smf} shows the SMF computed using \mcmodel{} 
     and \mtot{} for galaxies that live in low and high mass halos.  
     Figure \ref{fig:smf} shows that the impact of missing flux is more severe for  
     galaxies in high mass halos. 
     In Paper II of this series (Huang\etal in prep.), it will be demonstrated that 
     this occurs because galaxies in more massive halos have more extended stellar 
     envelopes than those in lower mass halos at fixed \mtot{}. 
     Figure \ref{fig:smf} also shows that the use of the HSC \texttt{cModel} 
     magnitude leads to a severe underestimation of \mstar{} at the high mass end 
     of SMF. 
     From the current \texttt{hscPipe}, this problem could relate to the intrinsic 
     limitation of simply model like \cmodel{} and the issue of over-subtracted 
     background. 
     Based on the 1-D surface brightness profiles in $i$-band, background subtraction
     does not seem to be the most serious problem for these $z>0.3$ galaxies 
     (at least not within 100 kpc). 
     And, in the next section, we will show that a significant fraction of these 
     1-D profiles are more extended in the outskirt than the de~Vaucouleurs profile, 
     therefore it is not surprising that \cmodel{} will systematically underestimate 
     their total flux.

@@

    As discussed in \S~\ref{ssec:mtotal}, even with deep HSC images,
    it is not trivial to clearly define and measure the ``total'' \mstar{} for 
    these massive systems, and the \mden{} profiles of these galaxies often extend 
    well beyond 100 kpc. 
    Is our fiducial 100 kpc radius sufficient to capture most of the flux associated 
    with these galaxies, or does one need to integrate out to even larger radii? 
    To answer this question, we attempt to capture more flux by integrating our 
    \mden{} profiles out to the edge of the image and use the highest \mstar{} 
    achieved during this process as \mmax{}.
    Although the \mden{} profiles become more uncertain at $>100$ kpc, \mmax{} helps 
    us quantify how much extra \mstar{} may be contained at radii greater than 100 kpc.  
    The right hand side of Figure \ref{fig:smf} shows the impact of using \mmax{} 
    instead of  \mtot{} on the SMF.  
    We find that a 100 kpc radius captures a majority of the galaxy mass and that the 
    impact of going from \mtot{} to \mmax{} is relatively small.

@@

        \item The SMF for $0.15 < z < 0.30$ galaxies from the \texttt{S82-MGC} sample
            \citep{Leauthaud2016} where \mstar{} is derived using 
            \texttt{iSEDfit} on PSF-corrected aperture photometry from \texttt{S82}. 
            They adopt the same IMF, dust model, and star-formation model as we do, 
            but use the \texttt{BC03} model instead. 
            Based on the test results in Appendix \ref{app:sed}, we shift this SMF by 
            0.08 dex to add their data to Figure~\ref{fig:smf}.

        \item The SMF derived from a SDSS-\textit{GALEX} sample of $z{\sim} 0.1$ 
            galaxies by \citet{Moustakas13}. 
            Total luminosities in \citet{Moustakas13} are based on SDSS \cmodel{} 
            magnitudes. 
            They use a \m2l{} that is derived via SED fitting using \texttt{iSEDfit} 
            with similar assumptions as the ones adopted here.

        \item The observed SMF for $z{\sim} 0.1$ SDSS galaxies from \citet{Bernardi2017}.          
            Total luminosities in \citet{Bernardi2017} are based on 2-D \texttt{SerExp} 
            models (\ser{}$+$ Exponential disk model; integrated to infinity) that 
            recover more flux compared to SDSS \cmodel{} magnitudes 
            (\citealt{Bernardi2013, Meert2015}). 
            They use a \m2l{} that is adopted from the SED fitting results in
            \citet{Mendel2014}. 
            This model also uses the \texttt{FSPS} stellar population model 
            \citep{FSPS}, assumes a \citet{Chabrier2003} IMF, and considers dust 
            extinction using the \citet{Calzetti2000} extinction law (the 
            ``dusty'' model).

    As mentioned above, our current SMF is subject to an additional 20\% uncertainty 
    that will be addressed in forthcoming work. 
    Hence, we do not attempt a detailed comparison with respect to previous works on 
    the SMF, reserving this for a future study. 
    Here, we simply note that the HSC SMF derived using \mtot{} is close to the one 
    derived by \citet{Bernardi2017} using SDSS data at $z{\sim}0.1$ and assuming 
    the \texttt{SerExp} models.  
    Our sample and the \citet{Bernardi2017} sample have different redshifts. 
    Without a more in-depth study, we cannot ascertain whether or not the apparent 
    agreement between the HSC SMF and the \citet{Bernardi2017} SMF indicates a global 
    lack of evolution in the galaxy SMF, or that other effects are at play 
    (difference between \mtot{} masses and \texttt{SerExp} masses) that have cancelled
    redshift evolution.  
    In future work, it will be interesting to perform a more consistent analysis to 
    search for redshift evolution in the galaxy SMF and to study whether or not 
    massive galaxies in HSC are well described by \texttt{SerExp} models.
